---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r load, echo=TRUE}
mytable <- read.table("activity.csv", header = TRUE, sep = ",", stringsAsFactors = TRUE)

```

Here is a summary table
```{r mysummary, results='asis'}
library(knitr)
kable(summary(mytable))
```


## What is mean total number of steps taken per day?
I create a new dataframe variable without NA's

```{r nona, echo=TRUE}
nonna<-na.omit(mytable)
kable(summary(nonna))
```

Using dplyr package I calculate the total number of steps per day

```{r grouping, echo=TRUE}
library(dplyr)

mygroup<-group_by(nonna,nonna$date)
steps_day<-summarise(mygroup,total=sum(steps), .groups= 'drop')
steps_day

hist(steps_day$total)

```

I calculate some basic measures of center

```{r computeeda, echo=TRUE}

mymean <- mean(steps_day$total)
mymedian <- median(steps_day$total)

```

The mean of the total number of steps is `r mymean` and the median is `r mymedian`


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
